---
title: "Triangle Sports Analytics Competition"
format: html
css: styles.css
page-layout: full
editor: 
  markdown: 
    wrap: 72
---

```{=html}
<!--
This Quarto page builds a scrolling one‑page website.  As visitors scroll down
the page they travel across a fixed background image of a basketball court while
a bouncing basketball follows them along the right side of the viewport.  The
layout and color palette are inspired by the dark, animated aesthetic of the
TreeHacks website (dark backdrop, simple white headings and vibrant accents)
【129026186528667†L27-L41】.  Custom CSS and JavaScript implement the
animation and styling.
-->
```

<!-- Ball element (positioned by scripts.js) -->

::: {#ball}
:::

<!-- Hero section -->

::: hero
<h1>Triangle Sports Analytics Competition 2026</h1>

<h2>Submissions due February 6 &#127936; Register [Here](https://forms.gle/5ZXVLvWgk8FsTtfJ8)</h2>

<p>Represent your school in data science and take home the title</p>
:::

<section id="all">

### About

The 2nd annual **Triangle Sports Analytics Competition** aims to bring together students from Duke, UNC, Chapel Hill, and NC State who love
sports analytics to compete in a prediction contest. All undergraduate and graduate students are eligible to compete. The scope of the competition is to predict all **ACC Men's Basketball** games between **February 7, 2026** and **March 7, 2026**. **Students may work individually or in a team of 2-5**.

<!-- ### Competition -->

<!-- - Point spread is the difference in points scored between Home and Away teams. Your job is to create a statistical model that predicts the point spread of ACC Men's Basketball games. [Click here to learn more](/task.html#Objective) -->

<!-- - Looking to go the extra mile? You can **optionally** submit prediction intervals as well. These will be judged separately. [Click here to learn more](/task.html#optional-advanced-objective-prediction-intervals) -->


```{r,echo=FALSE, message = FALSE,warning=FALSE}
library(DT)
library(tidyverse)
library(plyr)

# Read in Actual Spread
actual = read_csv("predictions/tsa_pt_spread_actual_2026.csv")
actual = actual[1:78,1:4]

# Read in Prediction Files from Students for Point Spread
pt1 = read_csv("predictions/tsa_pt_spread_UNCSigmaChiF24_2026.csv")[1:78,1:4]
pt2 = read_csv("predictions/tsa_pt_spread_Pandalytics_2026.csv")[1:78,1:4]
pt3 = read_csv("predictions/TSA_PT_spread_Ball_In_The_Family_2026.csv")[1:78,1:4]
pt4 = read_csv("predictions/tsa_pt_spread_arjun_2026 Arjun Trivedi.csv")[1:78,1:4]
pt5 = read_csv("predictions/tsa_pt_spread_Ball_Knower_2026 Christopher Dunevant.csv")[1:78,1:4]
pt6 = read_csv("predictions/tsa_pt_spread_Baracuda_Boys_2026 Joshua Harbaugh.csv")[1:78,1:4]
pt7 = read_csv("predictions/tsa_pt_spread_Beat_Dook_2026 Roshan Ragu.csv")[1:78,1:4]
pt8 = read_csv("predictions/tsa_pt_spread_Buzzer_Beaters_2026 Nicholas Hengsterman.csv")[1:78,1:4]
pt9 = read_csv("predictions/tsa_pt_spread_Caleb_Goated_Wilson_2026 Frank Thaingtham.csv")[1:78,1:4]
pt10 = read_csv("predictions/tsa_pt_spread_Caleb_s_Hammer_2026 Kenny Colindres-Carias.csv")[1:78,1:4]
pt11 = read_csv("predictions/tsa_pt_spread_CalebTruthers_2026 Tyler Watts.csv")[1:78,1:4]
pt12 = read_csv("predictions/tsa_pt_spread_CMMT_2026 Caleb Han.csv")[1:78,1:4]
pt13 = read_csv("predictions/tsa_pt_spread_Definitely_Not_Overfit_2026 Sean.csv")[1:78,1:4]
pt14 = read_csv("predictions/tsa_pt_spread_DerrickWhiteEnjoyer_2026 Nathan Honea.csv")[1:78,1:4]
pt15 = read_csv("predictions/tsa_pt_spread_devig_to_ball_knowledge_2026 Ethan Yountz.csv")[1:78,1:4]
pt16 = read_csv("predictions/tsa_pt_spread_Levin's_Lucky_Layups_2026.csv")[1:78,1:4]
pt17 = read_csv("predictions/tsa_pt_spread_fleiAnalytics_2026 Max Fleischer.csv")[1:78,1:4]
pt18 = read_csv("predictions/tsa_pt_spread_Freaky_Forecasts_2026 Eddy Ding.csv")[1:78,1:4]
pt19 = read_csv("predictions/tsa_pt_spread_Fuqua_Devils_2026 ruiting shao.csv")[1:78,1:4]
pt20 = read_csv("predictions/tsa_pt_spread_Gaussian_Eliminators_2026 - Sheet1 Aaron Siminou.csv")[1:78,1:4]
pt21 = read_csv("predictions/tsa_pt_spread_Grayson_Alpha_2026 - Sheet1 Ethan Mindlin.csv")[1:78,1:4]
pt22 = read_csv("predictions/tsa_pt_spread_Healthy_Kids_2026 Daniel Fulk.csv")[1:78,1:4]
pt23 = read_csv("predictions/tsa_pt_spread_Heels_Excel_2026 Riham.csv")[1:78,1:4]
pt24 = read_csv("predictions/tsa_pt_spread_HTN_Heaven_2026 - Sheet1 Ankita Karuturi.csv")[1:78,1:4]
pt25 = read_csv("predictions/tsa_pt_spread_I2A_2026 Adonias Ketema.csv")[1:78,1:4]
pt26 = read_csv("predictions/tsa_pt_spread_Lobryjakar - Sheet1 Jackson Tam.csv")[1:78,1:4]
pt27 = read_csv("predictions/tsa_pt_spread_midsters_2026 Gaurav Law.csv")[1:78,1:4]
pt28 = read_csv("predictions/tsa_pt_spread_MillerAndSons_2026 Christopher Miller.csv")[1:78,1:4]
pt29 = read_csv("predictions/tsa_pt_spread_moneyball_is_life_2026 Joseph Glasson.csv")[1:78,1:4]
pt30 = read_csv("predictions/tsa_pt_spread_Mustard_2026 - Sheet1 Daniel Wang.csv")[1:78,1:4]
pt31 = read_csv("predictions/tsa_pt_spread_Naman_2026 Naman Saboo.csv")[1:78,1:4]
pt32 = read_csv("predictions/tsa_pt_spread_Not_Cute_Anymore_2026 Hung-Chun Lu.csv")[1:78,1:4]
pt33 = read_csv("predictions/tsa_pt_spread_One_Ram_Band_2026 Case Redmond.csv")[1:78,1:4]
pt34 = read_csv("predictions/tsa_pt_spread_RedReckoning_2026 - Sheet1 Sam Brown.csv")[1:78,1:4]
pt35 = read_csv("predictions/tsa_pt_spread_template_Henri_Febre_2026 - Sheet1 Henri Febre.csv")[1:78,1:4]
pt36 = read_csv("predictions/tsa_pt_spread_Torvik_Tryhard_2026 Aaron J. Reed.csv")[1:78,1:4]
pt37 = read_csv("predictions/tsa_pt_spread_Trust_Me_Bro_Analytics_2026 Jason Pereira.csv")[1:78,1:4]
pt38 = read_csv("predictions/tsa_pt_spread_Twilight_Wolfpack_Analytics_2026 Ameen Ahmed.csv")[1:78,1:4]
pt39 = read_csv("predictions/tsa_pt_spread_Roll_the_Dice_2026 Ford Love.csv")[1:78,1:4]
pt40 = read_csv("predictions/tsa_pt_spread_BIOS_Bros_2026 Jonah Prober.csv")[1:78,1:4]

#Vector of Team Names for Point Spread
pt_teams = c("UNCSigmaChiF24", "Pandalytics", "Ball in the Family", "arjun", "Ball Knower",
          "Baracuda Boys","Beat Dook","Buzzer Beaters", "Caleb Goated Wilson","Caleb's Hammer",
          "CalebTruthers","CMMT","Definitely Not Overfit","DerrickWhiteEnjoyer","devig to ball knowledge",
          "Levin's Lucky Layups" , "fleiAnalytics","Freaky Forecasts", "Fuqua Devils","Gaussian Eliminators",
          "Grayson Alpha","Healthy Kids","Heels Excel","HTN Heaven","I2A",
          "Lobryjakar","MIDSTERS","MillerAndSons","(Money)ball is life","Mustard",
          "Naman","Not Cute Anymore","One Ram Band","RedReckoning","Henri Febre",
          "Torvik Tryhard","Trust Me Bro Analytics","Twilight Wolfpack Analytics","Roll the Dice","BIOS Bros")

#Merge Datasets
SPREAD=join_all(list(dplyr::rename(pt1,pt_spread_1=pt_spread),
                     dplyr::rename(pt2,pt_spread_2=pt_spread),
                     dplyr::rename(pt3,pt_spread_3=pt_spread),
                     dplyr::rename(pt4,pt_spread_4=pt_spread),
                     dplyr::rename(pt5,pt_spread_5=pt_spread),
                     dplyr::rename(pt6,pt_spread_6=pt_spread),
                     dplyr::rename(pt7,pt_spread_7=pt_spread),
                     dplyr::rename(pt8,pt_spread_8=pt_spread),
                     dplyr::rename(pt9,pt_spread_9=pt_spread),
                     dplyr::rename(pt10,pt_spread_10=pt_spread),
                     dplyr::rename(pt11,pt_spread_11=pt_spread),
                     dplyr::rename(pt12,pt_spread_12=pt_spread),
                     dplyr::rename(pt13,pt_spread_13=pt_spread),
                     dplyr::rename(pt14,pt_spread_14=pt_spread),
                     dplyr::rename(pt15,pt_spread_15=pt_spread),
                     dplyr::rename(pt16,pt_spread_16=pt_spread),
                     dplyr::rename(pt17,pt_spread_17=pt_spread),
                     dplyr::rename(pt18,pt_spread_18=pt_spread),
                     dplyr::rename(pt19,pt_spread_19=pt_spread),
                     dplyr::rename(pt20,pt_spread_20=pt_spread),
                     dplyr::rename(pt21,pt_spread_21=pt_spread),
                     dplyr::rename(pt22,pt_spread_22=pt_spread),
                     dplyr::rename(pt23,pt_spread_23=pt_spread),
                     dplyr::rename(pt24,pt_spread_24=pt_spread),
                     dplyr::rename(pt25,pt_spread_25=pt_spread),
                     dplyr::rename(pt26,pt_spread_26=pt_spread),
                     dplyr::rename(pt27,pt_spread_27=pt_spread),
                     dplyr::rename(pt28,pt_spread_28=pt_spread),
                     dplyr::rename(pt29,pt_spread_29=pt_spread),
                     dplyr::rename(pt30,pt_spread_30=pt_spread),
                     dplyr::rename(pt31,pt_spread_31=pt_spread),
                     dplyr::rename(pt32,pt_spread_32=pt_spread),
                     dplyr::rename(pt33,pt_spread_33=pt_spread),
                     dplyr::rename(pt34,pt_spread_34=pt_spread),
                     dplyr::rename(pt35,pt_spread_35=pt_spread),
                     dplyr::rename(pt36,pt_spread_36=pt_spread),
                     dplyr::rename(pt37,pt_spread_37=pt_spread),
                     dplyr::rename(pt38,pt_spread_38=pt_spread),
                     dplyr::rename(pt39,pt_spread_39=pt_spread),
                     dplyr::rename(pt40,pt_spread_40=pt_spread)),
                by=c("Date","Away","Home"),type="left")

SPREAD2 = SPREAD[,-(1:3)]

#MAE for predictions
mae.func=function(predict){
  mean(abs(actual$pt_spread-predict),na.rm=T)
}

eval = apply(SPREAD2,2,mae.func)

OUT_SPREAD = tibble(Team = pt_teams,MAE=round(eval,4)) |> arrange(MAE) |> mutate(Rank = round(rank(MAE))) |> select(Rank,everything())

```


### Leaderboard: Point Spreads

```{r,echo=FALSE}
datatable(OUT_SPREAD, rownames = FALSE, class = 'cell-border stripe',
          options=list(pageLength=40,dom="t")) 

```
Scoreboard updated on `r date()`.


```{r,echo=FALSE, message = FALSE,warning=FALSE}
# Read in Prediction Files from Students for Prediction Interval
pi1 = read_csv("predictions/tsa_pi_arjun_2026 Arjun Trivedi.csv")[1:78,1:5]
pi2 = read_csv("predictions/tsa_pi_Baracuda_Boys_2026 Joshua Harbaugh.csv")[1:78,1:5]
pi3 = read_csv("predictions/tsa_pi_BIOS_Bros_2026 Jonah Prober.csv")[1:78,1:5]
pi4 = read_csv("predictions/tsa_pi_Caleb_Goated_Wilson_2026 Frank Thaingtham.csv")[1:78,1:5]
pi5 = read_csv("predictions/tsa_pi_CalebTruthers_2026 Tyler Watts.csv")[1:78,1:5]
pi6 = read_csv("predictions/tsa_pi_Definitely_Not_Overfit_2026 Sean.csv")[1:78,1:5]
pi7 = read_csv("predictions/tsa_pi_devig_to_ball_knowledge_2026 Ethan Yountz.csv")[1:78,1:5]
pi8 = read_csv("predictions/tsa_pi_FIBA_Analytics_2026 Daniel Marin.csv")[1:78,1:5]
pi9 = read_csv("predictions/tsa_pi_Freaky_Forecasts_2026 Eddy Ding.csv")[1:78,1:5]
pi10 = read_csv("predictions/tsa_pi_Fuqua_Devils_2026 ruiting shao.csv")[1:78,1:5]
pi11 = read_csv("predictions/tsa_pi_Healthy_Kids_2026 Daniel Fulk.csv")[1:78,1:5]
pi12 = read_csv("predictions/tsa_pi_midsters_2026 Gaurav Law.csv")[1:78,1:5]
pi13 = read_csv("predictions/tsa_pi_MillerAndSons_2026 Christopher Miller.csv")[1:78,1:5]
pi14 = read_csv("predictions/tsa_pi_Mustard_2026 - Sheet1 Daniel Wang.csv")[1:78,1:5]
pi15 = read_csv("predictions/tsa_pi_Naman_2026 Naman Saboo.csv")[1:78,1:5]
pi16 = read_csv("predictions/tsa_pi_Not_Cute_Anymore_2026 Hung-Chun Lu.csv")[1:78,1:5]
pi17 = read_csv("predictions/tsa_pi_Torvik_Tryhard_2026 Aaron J. Reed.csv")[1:78,1:5]
pi18 = read_csv("predictions/tsa_pi_Twilight_Wolfpack_Analytics_2026 Ameen Ahmed.csv")[1:78,1:5]

#Vector of Team Names for Prediction Interval
pi_teams = c("Arjun", "Baracuda Boys","BIOS Bros","Caleb Goated Wilson","CalebTruthers",
             "Definitely Not Overfit","devig to ball knowledge","FIBA Analytics","Freaky Forecasts","Fuqua Devils",
             "Healthy Kids","MIDSTERS","MillerAndSons","Mustard","Naman",
             "Not Cute Anymore","Torvik Tryhard","Twilight Wolfpack Analytics")

#Merge Datasets
LB=join_all(list(dplyr::rename(pi1[,1:4],ci_lb_1=ci_lb),
                     dplyr::rename(pi2[,1:4],ci_lb_2=ci_lb),
                     dplyr::rename(pi3[,1:4],ci_lb_3=ci_lb),
                     dplyr::rename(pi4[,1:4],ci_lb_4=ci_lb),
                     dplyr::rename(pi5[,1:4],ci_lb_5=ci_lb),
                     dplyr::rename(pi6[,1:4],ci_lb_6=ci_lb),
                     dplyr::rename(pi7[,1:4],ci_lb_7=ci_lb),
                     dplyr::rename(pi8[,1:4],ci_lb_8=ci_lb),
                     dplyr::rename(pi9[,1:4],ci_lb_9=ci_lb),
                     dplyr::rename(pi10[,1:4],ci_lb_10=ci_lb),
                     dplyr::rename(pi11[,1:4],ci_lb_11=ci_lb),
                     dplyr::rename(pi12[,1:4],ci_lb_12=ci_lb),
                     dplyr::rename(pi13[,1:4],ci_lb_13=ci_lb),
                     dplyr::rename(pi14[,1:4],ci_lb_14=ci_lb),
                     dplyr::rename(pi15[,1:4],ci_lb_15=ci_lb),
                     dplyr::rename(pi16[,1:4],ci_lb_16=ci_lb),
                     dplyr::rename(pi17[,1:4],ci_lb_17=ci_lb),
                     dplyr::rename(pi18[,1:4],ci_lb_18=ci_lb)),
                by=c("Date","Away","Home"),type="left")

UB=join_all(list(dplyr::rename(pi1[,c(1,2,3,5)],ci_ub_1=ci_ub),
                     dplyr::rename(pi2[,c(1,2,3,5)],ci_ub_2=ci_ub),
                     dplyr::rename(pi3[,c(1,2,3,5)],ci_ub_3=ci_ub),
                     dplyr::rename(pi4[,c(1,2,3,5)],ci_ub_4=ci_ub),
                     dplyr::rename(pi5[,c(1,2,3,5)],ci_ub_5=ci_ub),
                     dplyr::rename(pi6[,c(1,2,3,5)],ci_ub_6=ci_ub),
                     dplyr::rename(pi7[,c(1,2,3,5)],ci_ub_7=ci_ub),
                     dplyr::rename(pi8[,c(1,2,3,5)],ci_ub_8=ci_ub),
                     dplyr::rename(pi9[,c(1,2,3,5)],ci_ub_9=ci_ub),
                     dplyr::rename(pi10[,c(1,2,3,5)],ci_ub_10=ci_ub),
                     dplyr::rename(pi11[,c(1,2,3,5)],ci_ub_11=ci_ub),
                     dplyr::rename(pi12[,c(1,2,3,5)],ci_ub_12=ci_ub),
                     dplyr::rename(pi13[,c(1,2,3,5)],ci_ub_13=ci_ub),
                     dplyr::rename(pi14[,c(1,2,3,5)],ci_ub_14=ci_ub),
                     dplyr::rename(pi15[,c(1,2,3,5)],ci_ub_15=ci_ub),
                     dplyr::rename(pi16[,c(1,2,3,5)],ci_ub_16=ci_ub),
                     dplyr::rename(pi17[,c(1,2,3,5)],ci_ub_17=ci_ub),
                     dplyr::rename(pi18[,c(1,2,3,5)],ci_ub_18=ci_ub)),
                by=c("Date","Away","Home"),type="left")

LB2=LB[,-c(1:3)]
UB2 = UB[,-c(1:3)]


#Measure Disqualification and PIW for each Group
DQ=rep(NA,dim(UB2)[2])
`%` = rep(NA,dim(UB2)[2])
eval=rep(NA,dim(UB2)[2])

for(i in 1:dim(UB2)[2]){
  check = mean(actual$pt_spread>LB2[,i] & actual$pt_spread<UB2[,i],na.rm=T)
  `%`[i]=check
  if (check < 0.7){
    DQ[i]="Yes"
  }else {
    DQ[i]="No"
    eval[i] = mean(UB2[!is.na(actual$pt_spread),i]-LB2[!is.na(actual$pt_spread),i])
  }
}

OUT_PIW = tibble(Team = pi_teams,`%`=round(`%`*100,2),DQ=DQ,PIW=round(eval,2)) |> arrange(PIW) |> mutate(Rank = round(min_rank(PIW))) |> select(Rank,everything())
```




### Leaderboard: Prediction Intervals

```{r,echo=FALSE}
datatable(OUT_PIW, rownames = FALSE, class = 'cell-border stripe',
          options=list(pageLength=20,dom="t"))  
```

Scoreboard updated on `r date()`.



### Questions?

Contact your school's organizer:

[Alexander Fisher (Duke)](mailto:alexander.fisher@duke.edu), [Elijah Meyer (NC State)](mailto:esmeyer2@ncsu.edu), [Mario Giacomazzo (UNC)](mailto:mgiacoma@email.unc.edu).
</section>

<!-- Include the animation script -->

```{=html}
<script src="scripts.js"></script>
```
