---
title: "Resources"
format: 
  html:
    toc: true
    toc-depth: 2
css: styles2.css
---

## Tutorial

The tutorial below will help you get started with basic data analysis in `R`. To follow along, you can download `R` and Rstudio. `R` is freely available at <http://www.r-project.org/>. RStudio, the popular IDE for `R`, is freely available at <https://posit.co/downloads/>.

::: callout-note
It's important to test the usefulness of sophisticated models against more basic alternatives. The following may serve as a simple baseline comparator.
:::

## Step 1: Collecting data

1a. Install a package to scrape NCAA data

```{r}
#| eval: false
install.packages("devtools")
devtools::install_github("lbenz730/ncaahoopR")
```

1b. Load `ncaahoopR` package and load `tidyverse`

```{r}
#| warning: false
#| message: false
library(ncaahoopR)
library(tidyverse)
```

1c. Glimpse at a particular team's schedule

```{r}
#| eval: false
#| echo: false
#| label: "hidden-1"

x <- get_schedule("Duke", "2024-25") %>%
  glimpse()

x %>%
  write_csv("data/duke-sample.csv")
```

```{r}
#| eval: false
# look at a team's schedule
duke_sample <- get_schedule("Duke", "2024-25")

duke_sample %>%
  glimpse()
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: "hidden-2"

duke_sample <- read_csv("data/duke-sample.csv")
duke_sample %>%
  glimpse()

```

1d. Check out documentation at <https://github.com/lbenz730/ncaahoopR>.

## Step 2: Basic prediction

Imagine you wish to predict the point spread in match-ups between Duke, UNC and NC State using data from Fall 2022. We can build a simple (poor) naive model that assumes each team scores a normally distributed amount of points per game.

```{r}
#| eval: false
pt_df = NULL

for(teamName in c("Duke", "UNC", "NC State")) {
pt_df = rbind(pt_df, get_schedule(teamName, "2022-23") %>%
  filter(date < "2023-01-01") %>% # look at only Fall games
  summarize(mean_pts = mean(team_score),
            var_pts = var(team_score)) %>%
  mutate(team = teamName))
}

pt_df 
```

```{r}
#| echo: false
#| label: "hidden-3"
#| warning: false
#| message: false
pt_df <-
  read_csv("data/pt-sample-df.csv")

pt_df
```

Using this, we can make naive predictions about the outcome of each matchup.

```{r}
getCI95 = function(m, s) {
  return(toString(
    c(m - (qnorm(0.975) * s), m + (qnorm(0.975) * s))
  ))
}
  
lookup <- c(team1 = "V1", team2= "V2")

combn(pt_df$team, 2) %>%
  t() %>%
  as.data.frame() %>%
  rename(all_of(lookup)) %>%
  rowwise() %>%
  mutate(pt_spread = 
           pt_df$mean_pts[pt_df["team"] == team1] - 
            pt_df$mean_pts[pt_df["team"] == team2]) %>%
  mutate(spread_sd = 
           sqrt(pt_df$var_pts[pt_df["team"] == team1] +
            pt_df$var_pts[pt_df["team"] == team2])) %>%
  mutate(spread_CI_95 = getCI95(pt_spread, spread_sd)) %>%
  select(-spread_sd)
```

## Further reading

Here are a list of online articles that may be helpful in this competition.

-- [Creating a College Basketball Metric to Predict Point Spreads for March MadnessArticle](https://medium.com/@jriordan1/creating-a-college-basketball-metric-to-predict-point-spreads-for-march-madness-02bbdf048e99)

-- [Confidence vs Prediction Intervals: Understanding the Difference](https://www.datacamp.com/blog/confidence-intervals-vs-prediction-intervals)

